COMPAS Race Analysis

### 2022-04-28 race compas analysis.Rmd

```{python pre-processing accuracy score} 
acc_REW = accuracy_score(y_test, y_pred_REW)
print(f'[Reweighting] The test accuracy of the algorithm is: {acc_REW: .2%}')
```

```{python pre-processing confusion matrix}
cf_matrix = confusion_matrix(y_test, y_pred_REW)
make_confusion_matrix(cf_matrix, "[Reweighting]")
plt.show()
```

@@

print(f'[Reweighting] The statistical parity difference is {stat_par_diff_RW: .2}')
```

@@

print(f'[Reweighting] The equal opportunity difference is {eq_opp_diff_RW: .2}')
```

@@

print(f'[Reweighting] The generalized entropy error is {gen_entr_error_RW: .2}')
```

@@

```{python pre-processing fairness metrics plot}
plot_fair_metrics([stat_par_diff_RW, eq_opp_diff_RW, gen_entr_error_RW], 'Reweighting')
plt.show()
```

>>>>

```{python pre-processing accuracy score} 
acc_REW = accuracy_score(y_test, y_pred_REW)
print(f'[Reweighing] The test accuracy of the algorithm is: {acc_REW: .2%}')
```

```{python pre-processing confusion matrix}
cf_matrix = confusion_matrix(y_test, y_pred_REW)
make_confusion_matrix(cf_matrix, "[Reweighing]")
plt.show()
```

@@

print(f'[Reweighing] The statistical parity difference is {stat_par_diff_RW: .2}')
```

@@

print(f'[Reweighing] The equal opportunity difference is {eq_opp_diff_RW: .2}')
```

@@

print(f'[Reweighing] The generalized entropy error is {gen_entr_error_RW: .2}')
```

@@

```{python pre-processing fairness metrics plot}
plot_fair_metrics([stat_par_diff_RW, eq_opp_diff_RW, gen_entr_error_RW], 'Reweighing')
plt.show()
```
